DNSKEY Management

### 2012-12-04 paper/paper.tex
tea time.

>>>>

\subsection{Computing power}
DNSSEC does not only require a higher coordination among the three R's, it also increases the strain on the computing infrastructure of a registrar when the size and quantity of the  zones it manages grow: updates to a zone or key rollovers require cryptographic signing operations that are orders of magnitude more expensive than simply updating the DNS record. Even with improvements like incremental signing, the computational requirements are significant and must be considered when a registrar whishes to enable DNSSEC.
%TODO find good ref on this.
